A thesis draft

### 2018-11-19 res/sections/08-Background.tex
80 columns, preliminar check

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 with the paper~\cite{peterson2003blueprint}, in which
is described an overlay network that allow services to access different slices
of overlay's resources and in which overlay management services run in their
own slice. This idea was be refined during time and
in~\cite{alliance2016description} the design of network slicing is based on a
three-layers model, as depicted in
Figure~\ref{chap:background:img:network_slicing}.

@@

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
  \begin{tabular}{p{4,5cm}|p{5,5cm}|p{5cm}}
\textbf{Attribute}                                                    & 
\textbf{LTE capability}                                                          
                                                                           & 
\textbf{Improvement needed to meet NGMN requirements}                 \\ \hline
\textbf{Data rate (per user)}                                         & Up to 
100 Mb/s on average Peaks of 600 Mb/s (Cat 11/12).                               
                                                                     & 10X 
expected on average and peak rates and 100X expected on cell edge \\
\textbf{End-to-end latency}                                           & 10 ms 
for two-way RAN (pre-scheduled). Typically, up to 50 ms end-to-end if other 
factors are considered (e.g., transmission, CN, internet, proxy servers). & 10X 
(smaller)                                                         \\
\textbf{Mobility}                                                     & 
Functional up to 350 km/h (for certain bands up to 500 km/h). No support for 
civil aviation.                                                                & 
1.5X                                                                  \\
\textbf{\begin{tabular}[c]{@{}l@{}}Connection\\ density\end{tabular}} & 
Typically $\sim$2,000 active users/km2.                                          
                                                                           & 
100X                                                                 
\end{tabular}%
}
\caption[5G improvement over LTE]{An extract from the official 5G white paper 
illustrating the improvements of 5G relatively to LTE connections.}
\label{chap:intro:table:ltevs5g}
\end{table}

>>>>

\section{Network slicing}
A network slice can be defined as a logical virtual network, tailored for a
given use case, on the top a common network using technologies such as
Software-Defined Networking and Network Function Chaining that allows network
softwarization~\cite{ordonez2017network}. The notion of separated virtual
networks deployed on the same infrastructure is not new, e.g. VPN, but it has
some specifics that make it a novel idea. The concept of network slicing was
first introduced in 2002 with the in\cite{peterson2003blueprint}, where
is described an overlay network that allows services to access different slices
of overlay's resources and in which overlay management services run in their
own slice. Lately this idea has be refined  and
in\cite{alliance2016description} the design of network slicing was based on a
three-layers model, as depicted in
Figure~\ref{chap:background:img:network_slicing}.

@@

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
  \begin{tabular}{p{4,5cm}|p{5,5cm}|p{5cm}}
\textbf{Attribute}                                                    & 
\textbf{LTE capability}

                                                                           & 
\textbf{Improvement needed to meet NGMN requirements}                 \\ \hline
\textbf{Data rate (per user)}                                         & Up to 
100 Mb/s on average Peaks of 600 Mb/s (Cat 11/12).

                                                                     & 10X 
expected on average and peak rates and 100X expected on cell edge \\
\textbf{End-to-end latency}                                           & 10 ms 
for two-way RAN (pre-scheduled). Typically, up to 50 ms end-to-end if other 
factors are considered (e.g., transmission, CN, internet, proxy servers). & 10X 
(smaller)                                                         \\
\textbf{Mobility}                                                     & 
Functional up to 350 km/h (for certain bands up to 500 km/h). No support for 
civil aviation.                                                                
& 
1.5X                                                                  \\
\textbf{\begin{tabular}[c]{@{}l@{}}Connection\\ density\end{tabular}} & 
Typically $\sim$2,000 active users/km2.

                                                                           & 
100X                                                                 
\end{tabular}%
}
\caption[5G improvement over LTE]{An extract from the official 5G white paper 
illustrating the improvements of 5G relatively to LTE connections.}
\label{chap:intro:table:ltevs5g}
\end{table}
